You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-24 paper/paper.tex
minor changes..

\subsubsection{Out of Domain Monolingual Parallel Data}

\subsection{Initial Comparison}
\begin{itemize}
  \item List the various systems we evaluate (e.g. varying LM size, etc...)
  \item Plot BLEU and PINC scores for the various systems
\end{itemize}

>>>>

\subsubsection{Out of Domain Monolingual Parallel Data}
As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of doimain parallel text, with an in-domain
language model consisting of Shakespeare's 37 plays.

\subsection{Comparison Using Automatic Evaluation Metrics}
\begin{itemize}
  \item List the various systems we evaluate (e.g. varying LM size, etc...)
  \item Plot BLEU and PINC scores for the various systems
\end{itemize}
